---
title: "assignment_2"
author: "sai sree pulimamidi"
date: "2022-10-26"
output:
  html_document: default
  word_document: default
  pdf_document: default
---

***Loading all the required packages***
```{r}
library("VIM")
library("ISLR")
library("caret")
library("class")
library("e1071")
library("ggplot2")
library("corrplot")
library("dplyr")
```


***Setting up working directory and loading data***
```{r}

online_retail <- read.csv("C:/Users/sudhakar/Downloads/Online_Retail (1).csv")
```


***1
```{r}
data_country <- as.data.frame(table(online_retail$Country))

data_country$Percentage <- data_country$Freq/nrow(online_retail) * 100

colnames(data_country) <- c("Country", "Count", "Percentage")

data_country[data_country$Percentage > 1,]
```
*Countries accounting for more than 1% of the total transactions are EIRE, France, Germany and United Kingdom.*
/vspace{1mm}/newline

***2. Adding new attribute "TransactionValue" which is the product of Quantity and UnitPrice***
```{r}
online_retail$TransactionValue <- online_retail$Quantity * online_retail$UnitPrice
```
*By adding this new attribute we can now calculate the value of the transactions based on our requirement.*
/vspace{1mm}/newline

***3. Using the newly created variable, TransactionValue, showing the breakdown of transaction values by countries with total transaction exceeding 130,000 British Pound***
```{r}
online_retail %>% select(TransactionValue,Country) %>% group_by(Country) %>% summarise(Total = sum(TransactionValue)) %>% filter(Total >= 130000) %>% arrange((desc(Total)))
```
*There are total 6 countries where the transaction value exceeds 130,000 British Pound and the highest among them is "United Kingdom".*
/vspace{1mm}/newline

***4. Converting Invoice Date into a POSIXlt object***
```{r}
Temp=strptime(online_retail$InvoiceDate,format='%m/%d/%Y %H:%M',tz='GMT')
head(Temp)

#New_Invoice_Date
online_retail$New_Invoice_Date <- as.Date(Temp)

online_retail$New_Invoice_Date[20000]- online_retail$New_Invoice_Date[10]

#Invoice_Day_Week
online_retail$Invoice_Day_Week= weekdays(online_retail$New_Invoice_Date)

#New_Invoice_Hour
online_retail$New_Invoice_Hour = as.numeric(format(Temp, "%H"))

#New_Invoice_Month
online_retail$New_Invoice_Month = as.numeric(format(Temp, "%m"))
```

***4(a). Percentage of transactions (by numbers) by days of the week***
```{r}
online_retail %>% group_by(Invoice_Day_Week) %>% summarise(count=n()) %>% mutate(percentage=count/nrow(online_retail)*100)
```

***4(b). Percentage of transactions (by transaction volume) by days of the week***
```{r}
online_retail %>% group_by(Invoice_Day_Week) %>% summarise(Total = sum(TransactionValue)) %>% mutate(Percentage = Total/sum(Total)*100)
```

***4(c). Percentage of transactions (by transaction volume) by month of the year***
```{r}
online_retail %>% group_by(New_Invoice_Month) %>% summarise(Total = sum(TransactionValue)) %>% mutate(Percentage = Total/sum(Total) * 100)
```

***4(d). The date with the highest number of transactions from Australia***
```{r}
online_retail %>% filter(Country =="Australia") %>% group_by(New_Invoice_Date) %>% summarise(Total_Count = n()) %>% arrange((desc(Total_Count)))
```
*As we can see from above on 2011-06-15 Australia has recorded the highest number of transactions i.e. 139 Transactions.*
/vspace{1mm}/newline

***5. Plot the histogram of transaction values from Germany***
```{r}
Germany <- online_retail %>% filter(Country == "Germany") %>% group_by(New_Invoice_Month) %>% summarise(Total=sum(TransactionValue)) 

hist(Germany$Total, main = "Transaction Values of Germany", xlab="Total per month", ylab="Frequencies")
```

***6(a). Customer who had highest number of transactions***
```{r}
online_retail %>% group_by(CustomerID) %>% select(CustomerID) %>% filter(!is.na(CustomerID)) %>% summarise(n_count = n()) %>% arrange((desc(n_count)))
```
*The CustomerID 17841 had the highest number of transactions amongst others with a total of 7983 transactions.*
/vspace{1mm}/newline

***6(b). Most valuable customer with the highest total sum of transactions***
```{r}
online_retail %>% group_by(CustomerID) %>% select(CustomerID, TransactionValue) %>% filter(!is.na(CustomerID)) %>% summarise(Spending_max = sum(TransactionValue)) %>% arrange((desc(Spending_max)))
```
*The CustomerID 14646 is the most valuable customer with the highest spending sum of 279,489.020 British Sterling Pound.*
/vspace{1mm}/newline

***7. Percentage of missing values for each variable in the dataset***
```{r}
colMeans(is.na(online_retail)*100)
```
*We can observe that CustomerID is the only attribute with 24.9266% of NAs in the entire dataset.*
/vspace{1mm}/newline

***8. The number of transactions with missing CustomerID records by Countries***
```{r}
online_retail %>% filter(is.na(CustomerID)) %>% group_by(Country) %>% count()
``` 
*There are in total 8 countries and 1 unspecified country in the entire dataset which has NA values in them amongst these United Kingdom is the country with highest NA records of 133,600 rows.*
/vspace{1mm}/newline

***9. On average, how often the costumers comeback to the website for their next shopping?***
```{r}
Diff_Days <- online_retail %>% select(CustomerID,New_Invoice_Date) %>% group_by(CustomerID) %>% distinct(New_Invoice_Date) %>% arrange(desc(CustomerID)) %>%  mutate(Days_Between = New_Invoice_Date-lag(New_Invoice_Date)) %>% filter(!is.na(Days_Between)) 

Diff_Days

mean(Diff_Days$Days_Between)
```
*On an average approximately for every 38 days customers come back to the website for their next shopping.*
/vspace{1mm}/newline

***10. Return rate of goods purchased by the customers from France***
```{r}
F_Cancel <- online_retail %>% filter(Country=="France",Quantity<0) %>% count()

F_Total <- online_retail %>% filter(Country=="France") %>% count()

Return_Percentage_France <- F_Cancel/F_Total*100
Return_Percentage_France
```
*The return rate of customers who made purchases in France is 1.741264%.*
/vspace{1mm}/newline

***11. The product that has generated the highest revenue for the retailer***
```{r}
online_retail %>% select(StockCode,TransactionValue) %>% group_by(StockCode) %>%  summarise(Total=sum(TransactionValue)) %>% arrange((desc(Total))) 
```
*The product with the StockCode as "DOT" is the one which has generated highest revenue to the retailer i.e. 206,245.48 British Sterling Pound.*
/vspace{1mm}/newline

***12. Unique Customers in the dataset***
```{r}
online_retail %>% select(CustomerID) %>% unique() %>% count()
```
*In total there are 4,373 unique customers in the dataset.*